Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards

### 2024-04-23 paper/paper.qmd
fixed month data

>>>>

The analysis of these three datasets will be carried out using the statistical programming language `R` [@citeR], using the `tidyverse`[@citetidy], `here`[@citehere], and `readxl`[@citexl] packages. The figures and tables in the paper are generated using the, respectively, `ggplot2`[@citegg] and `knitr`[@citeknitr] packages.
```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)

```
